\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{enumitem}
\usepackage[margin=0.8in,top=0.8in,bottom=0.8in]{geometry}
\usepackage{hyperref}
\usepackage{titling}
\usepackage{array}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{academicons}
\usepackage{multicol}
\usepackage{changepage}
\usepackage{microtype}

% Define colors
\definecolor{headercolor}{RGB}{0, 51, 102}
\definecolor{subheadercolor}{RGB}{70, 70, 70}
\definecolor{linkcolor}{RGB}{0, 102, 204}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    citecolor=linkcolor
}

% Section title format with proper spacing
\titleformat{\section}
    {\large\bfseries\color{headercolor}}
    {}
    {0em}
    {}
    [\vspace{-0.3em}\color{headercolor}\titlerule\vspace{-0.5em}]

\titleformat{\subsection}
    {\normalsize\bfseries\color{subheadercolor}}
    {}
    {0em}
    {}
    [\vspace{-0.5em}]

% Custom commands for better formatting
\newcommand{\CVItem}[2]{
    \noindent\textbf{#1} \hfill #2\\
}

\newcommand{\CVSubItem}[1]{
    \vspace{-0.8em}
    \begin{adjustwidth}{0em}{0em}
    \textit{#1}
    \end{adjustwidth}
    \vspace{0.3em}
}

% Adjust list spacing
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=1.5em, parsep=0pt}
\setlist[enumerate]{noitemsep, topsep=0pt, leftmargin=1.5em, parsep=0pt}

% Prevent widows and orphans
\widowpenalty=10000
\clubpenalty=10000

\begin{document}
\pagestyle{empty}

% Header with name and contact information
\begin{center}
    {\LARGE \textbf{\color{headercolor}Yonghan Kwon}}\\[2mm]
    {\large PhD in Biostatistics and Computing}\\[1mm]
    Yonsei University, Seoul, South Korea\\[2mm]
    
    \begin{tabular}{c c}
        \faEnvelope\ \href{mailto:yonghankwon0@yuhs.ac}{yonghankwon0@yuhs.ac} & 
        \faEnvelope\ \href{mailto:yonghankwon0@gmail.com}{yonghankwon0@gmail.com} \\[1mm]
        \faLinkedin\ \href{https://www.linkedin.com/in/yonghan-kwon-84693a171}{LinkedIn} & 
        \aiGoogleScholar\ \href{https://scholar.google.com/citations?user=ED4nS-8AAAAJ}{Google Scholar}
    \end{tabular}
\end{center}

\vspace{0.3em}

% Research Interests
\begin{center}
    \colorbox{gray!10}{
        \begin{tabular}{c}
            \textbf{Research Interests:} Biostatistics $\cdot$ Machine Learning $\cdot$ Network Analysis $\cdot$ Radiology $\cdot$ Radiomics
        \end{tabular}
    }
\end{center}

\vspace{0.3em}

% Education Section
\section*{Education}

\CVItem{Yonsei University, South Korea}{Mar 2022 -- Aug 2025}
\CVSubItem{Doctor of Philosophy in Biostatistics and Computing}
\noindent\textit{Thesis:} Adaptive Group-Laplacian Regularization with Stability Selection: A Robust Approach to Variable Selection

\vspace{0.5em}

\CVItem{Yonsei University, South Korea}{Mar 2020 -- Feb 2022}
\CVSubItem{Master's Degree in Biostatistics and Computing}
\noindent\textit{Thesis:} Stability selection for LASSO with weights based on AUC

\vspace{0.5em}

\CVItem{Kyonggi University, South Korea}{2014 -- 2020}
\CVSubItem{Bachelor's Degree in Applied Statistics}

% Experience Section
\section*{Research Experience}

\CVItem{Postdoctoral Researcher}{Sep 2025 -- Present}
\CVSubItem{Department of Radiology, Yonsei University, South Korea}
\vspace{-0.5em}
\begin{itemize}
    \item Conducting advanced radiomics and biostatistics research under the supervision of Younghan Lee, MD, PhD and Kyunghwa Han, PhD
\end{itemize}

\vspace{0.3em}

\CVItem{Researcher}{Oct 2020 -- Aug 2025}
\CVSubItem{Yonsei University, South Korea}
\vspace{-0.5em}
\begin{itemize}
    \item Conducting radiology research at CCIDS under the guidance of Kyunghwa Han, PhD
\end{itemize}

\vspace{0.3em}

\CVItem{Student Intern}{Jun 2019 -- Oct 2019}
\CVSubItem{CCADD, Seoul National University, South Korea}
\vspace{-0.5em}
\begin{itemize}
    \item Contributed to dimensionality reduction modeling for clinical trial feasibility assessment using EMR data under Howard Lee, PhD
\end{itemize}

\vspace{0.3em}

\CVItem{Student Intern}{Mar 2019 -- Jun 2019}
\CVSubItem{Kyonggi University, South Korea}
\vspace{-0.5em}
\begin{itemize}
    \item Learned preprocessing microbiome data and statistical tests under Yujin Chung, PhD
\end{itemize}

% Teaching Experience Section
\section*{Teaching Experience}

\CVItem{Guest Lecturer}{Fall 2025}
\CVSubItem{Graduate School of Public Health, Yonsei University, South Korea}
\vspace{-0.5em}
\begin{itemize}
    \item Course: Big Data and Data Mining
    \item Topic: Data Mining Algorithms (1) -- Classification Analysis
    \item Covered logistic regression, CART, and Random Forest methods
    \item Delivered lecture on November 4, 2025 (Week 9)
\end{itemize}

% Publications Section
\section*{Peer-Reviewed Publications}
{\small \textit{* Underlined authors indicate first authors}}\\[0.3em]

\begin{enumerate}[label={\color{headercolor}[\arabic*]}]
    \setlength\itemsep{0.3em}
    \item \underline{J Kim}, EJ Lee, H Yoon, K Han, \textbf{Y Kwon}, H Koh, YW Kim, MJ Lee. (2026).
    Associations of Ultrasound-Derived Fat Fraction and MRI PDFF Measurements: A Prospective Study in Pediatric Patients With Suspected MASLD.
    \textit{American Journal of Roentgenology}. \href{https://doi.org/10.2214/AJR.25.34230}{[DOI]}

    \item \underline{J Lee}, J Go, SJ Lee, \textbf{Y Kwon}, NH Kim, JY Kim, HS Park. (2025).
    Comparative study of mastectomy using conventional techniques, multiport and single-port robotic surgical systems.
    \textit{Cancer Research and Treatment}. \href{https://doi.org/10.4143/crt.2025.115}{[DOI]}

    \item \underline{SM Ahn}, DC Jung, MH Moon, JW Lee, K Han, \textbf{Y Kwon}. (2025).
    A potential imaging-based predictor for renal functional outcomes after partial nephrectomy for localized renal masses.
    \textit{BMC Urology}, 25(1), 244. \href{https://doi.org/10.1186/s12894-025-01907-3}{[DOI]}

    \item \underline{JE Lee}, NY Kim, YH Kim, \textbf{Y Kwon}, S Kim, K Han, YJ Suh. (2025).
    Long-term prognostic implications of thoracic aortic calcification on CT using artificial intelligence–based quantification in a screening population: a two-center study.
    \textit{American Journal of Roentgenology}, 1--15. \href{https://doi.org/10.2214/AJR.25.32697}{[DOI]}

    \item \underline{J Kim}, MJ Lee, HJ Lim, \textbf{Y Kwon}, K Han, H Yoon. (2025).
    Pediatric reference values for total psoas muscle area in Korean children and adolescents.
    \textit{Frontiers in Pediatrics}, 12, 1443523. \href{https://doi.org/10.3389/fped.2024.1443523}{[DOI]}

    \item \underline{YJ Suh}, K Han, \textbf{Y Kwon}, H Kim, S Lee, SH Hwang, MH Kim, HJ Shin, et al. (2024).
    Computed Tomography Radiomics for Preoperative Prediction of Spread Through Air Spaces in the Early Stage of Surgically Resected Lung Adenocarcinomas.
    \textit{Yonsei Medical Journal}, 65(3), 163. \href{https://doi.org/10.3349/ymj.2023.0368}{[DOI]}

    \item \underline{\textbf{Y Kwon}}, K Han. (2023).
    Development and Validation of a Prediction Model: Application to Digestive Cancer Research.
    \textit{Journal of Digestive Cancer Research}, 11(3), 157--164. \href{https://doi.org/10.52927/jdcr.2023.11.3.157}{[DOI]}

    \item \underline{S Chang}, K Han, \textbf{Y Kwon}, L Kim, S Hwang, H Kim, BW Choi. (2023).
    T1 map-based radiomics for prediction of left ventricular reverse remodeling in patients with nonischemic dilated cardiomyopathy.
    \textit{Korean Journal of Radiology}, 24(5), 395. \href{https://doi.org/10.3348/kjr.2023.0065}{[DOI]}

    \item \underline{\textbf{Y Kwon}}, K Han, YJ Suh, I Jung. (2023).
    Stability selection for LASSO with weights based on AUC.
    \textit{Scientific Reports}, 13(1), 5207. \href{https://doi.org/10.1038/s41598-023-32517-4}{[DOI]}

    \item \underline{SH Chun}, YJ Suh, K Han, \textbf{Y Kwon}, AY Kim, BW Choi. (2022).
    Deep learning-based reconstruction on cardiac CT yields distinct radiomic features compared to iterative and filtered back projection reconstructions.
    \textit{Scientific Reports}, 12(1), 15171. \href{https://doi.org/10.1038/s41598-022-19546-1}{[DOI]}

    \item \underline{HS Park}, J Lee, JY Kim, JM Park, \textbf{Y Kwon}. (2022).
    A prospective randomized study to compare postoperative drainage after mastectomy using electrosurgical bipolar systems and conventional electro-cautery.
    \textit{Journal of Breast Cancer}, 25(4), 307. \href{https://doi.org/10.4048/jbc.2022.25.e29}{[DOI]}

    \item \underline{JA Gim}, \textbf{Y Kwon}, HA Lee, KR Lee, S Kim, Y Choi, YK Kim, H Lee. (2020).
    A Machine Learning-Based Identification of Genes Affecting the Pharmacokinetics of Tacrolimus Using the DMET$^{TM}$ Plus Platform.
    \textit{International Journal of Molecular Sciences}, 21(7), 2517. \href{https://doi.org/10.3390/ijms21072517}{[DOI]}
\end{enumerate}

% Presentations Section
\section*{Conference Presentations}

\subsection*{Oral Presentations}
{\small \textit{* Underlined authors presented the work}}\\[0.3em]

\begin{enumerate}[label={\color{subheadercolor}[\arabic*]}]
    \setlength\itemsep{0.3em}
    \item \underline{\textbf{Y Kwon}}, K Han, YJ Suh, I Jung. (2025).
    Adaptive Group-Laplacian Regularization with Stability Selection: A Robust Approach to Variable Selection.
    \textit{Korean Statistical Society Summer Conference}.

    \item \underline{\textbf{Y Kwon}}, J Kim, H Yoon, Y Kim, H Koh, E Lee, K Han, M Lee. (2025).
    Optimal Minimal Number for the Proper Acquisition of Multisample Ultrasound Point Shear Wave Elastography for Evaluating Pediatric Liver in Consideration With the Effect of Breathing.
    \textit{The 56th Annual Congress of Korean Society of Ultrasound in Medicine}.
    
    \item \underline{H Yoon}, J Kim, K Han, \textbf{Y Kwon}, Y Kim, H Koh, E Lee, M Lee. (2025).
    Optimum Minimal Number for Proper Acquisition of Ultrasound-Derived Fat Fraction in Pediatric Patients With Suspicious Fatty Liver Disease in Consideration With the Effect of Breathing.
    \textit{The 56th Annual Congress of Korean Society of Ultrasound in Medicine}.
    
    \item \underline{J Kim}, H Yoon, K Han, \textbf{Y Kwon}, H Koh, Y Kim, E Lee, M Lee. (2025).
    Correlation Between Ultrasound Derived Fat Fraction and Proton Density Fat Fraction for Evaluating Pediatric Hepatic Steatosis With Consideration of the Breathing Effect.
    \textit{The 56th Annual Congress of Korean Society of Ultrasound in Medicine}.
    
    \item \underline{S Lee}, K Han, \textbf{Y Kwon}, YJ Suh. (2024).
    Development and Validation of a Machine-Learning Model for Synthetic Hematocrit Estimation in Cardiac MRI without Blood Sampling.
    \textit{Korean Congress of Radiology (KCR)}, October 3.
    
    \item \underline{JE Lee}, N Kim, \textbf{Y Kwon}, K Han, YJ Suh. (2024).
    Long-term prognostic implications of AI-based thoracic aorta calcification quantification in a screening population: a multicenter study.
    \textit{Radiological Society of North America Annual Meeting}.
\end{enumerate}

\subsection*{Poster Presentations}
{\small \textit{* Underlined authors presented the work}}\\[0.3em]
\begin{enumerate}[label={\color{subheadercolor}[\arabic*]}]
    \setlength\itemsep{0.3em}
    \item \underline{M Kim}, \textbf{Y Kwon}, I Jung. (2025).
    Evaluating Automated Calibration for Stability Selection in Penalized Logistic Regression.
    \textit{Korean Society of Health Informatics and Statistics Conference}.

    \item \underline{\textbf{Y Kwon}}, K Han, YJ Suh, I Jung. (2025).
    Adaptive Group-Laplacian Regularization with Stability Selection: A Robust Approach to Variable Selection.
    \textit{IASC-ARS 2025 (International Association for Statistical Computing - Asian Regional Section)}.
    
    \item \underline{\textbf{Y Kwon}}, K Han, YJ Suh, I Jung. (2023).
    Comparative analysis of LASSO and Group LASSO: performance, practicality, and application.
    \textit{Korean Statistical Society Winter Conference}.
    
    \item \underline{Y So}, \textbf{Y Kwon}, K Han, I Jung. (2023).
    Comparison of variable selection through the combination of sub-sampling method and weighting method with imbalanced data.
    \textit{Korean Statistical Society Summer Conference}.
    
    \item \underline{R Lee}, \textbf{Y Kwon}, K Han, I Jung. (2022).
    Random survival forest-based weighted variable selection for survival data.
    \textit{Korean Statistical Society Summer Conference}.
    
    \item \underline{\textbf{Y Kwon}}, K Han, I Jung. (2021).
    Stability selection for LASSO with weights based on AUC.
    \textit{Korean Statistical Society Fall Conference}.
    
    \item \underline{Y Jeon}, \textbf{Y Kwon}, H Lee. (2019).
    A dimensionality reduction model to increase the efficiency and accuracy of clinical trial feasibility assessment using electronic medical records.
    \textit{Korean Society of Medical Informatics Fall Conference}.
\end{enumerate}
% Awards and Grants Section
\section*{Grants \& Awards}

\subsection*{Research Grants}
\noindent\textbf{Research Subsidies for Ph.D. Candidates} \hfill Sep 2024 -- Aug 2026\\
\textit{Development and clinical application of variable selection methodology via network-based clustering of high-dimensional radiomics data}\\
\textbf{Award Amount:} 50,000,000 KRW (2-year grant)

\subsection*{Awards \& Honors}
\begin{itemize}[leftmargin=1em]
    \setlength\itemsep{0.2em}
    \item \textbf{Graduate Student Outstanding Paper Award} (Encouragement) -- Yonsei University College of Medicine (2022)
    \item \textbf{Poster Award} (3rd place/25 teams) -- Korean Statistical Society Summer Conference (2022)
    \item \textbf{Poster Award} (3rd place/42 teams) -- Korean Statistical Society Fall Conference (2021)
    \item \textbf{3rd Prize} -- Seoul National University Medical AI Competition (2020)
    \item \textbf{2nd Prize} -- Data Analysis Contest, Kyonggi University (2019)
    \item \textbf{Excellence Award} -- 7th University Student Reliability Project Contest (2017)
\end{itemize}

% Scholarships Section
\section*{Scholarships}

\begin{multicols}{2}
\subsection*{Yonsei University (2020--2024)}
\begin{itemize}[leftmargin=1em]
    \setlength\itemsep{0.1em}
    \item Yonsei Graduate Fellowship (YGF): 5,000,000 KRW
    \item Academic Research Fellowship (ARF): 1,000,000 KRW
    \item Chief Professor GSRA: 5,000,000 KRW
    \item Work/Teaching Assistantships: 22,100,000 KRW
    \item BK21 Plus Scholarship: 600,000 KRW
\end{itemize}

\columnbreak

\subsection*{Kyonggi University (2018--2019)}
\begin{itemize}[leftmargin=1em]
    \setlength\itemsep{0.1em}
    \item Academic Scholarship: 1,932,000 KRW
    \item KGU Recommended Type A: 1,500,000 KRW
    \item Academic/Employment Scholarships: 1,300,000 KRW
\end{itemize}
\end{multicols}

\vspace{0.5em}

% Languages Section
\section*{Languages}
\begin{itemize}[leftmargin=1em]
    \item \textbf{Korean:} Native proficiency
    \item \textbf{English:} Professional working proficiency
\end{itemize}

\end{document}